### 2017-02-28 R/ITHIM2.Rmd

```{r tilePlot, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
ITHIM <- createITHIM()
tilePlot(ITHIM, n = 50)
```

>>>>

```{r tilePlot, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1, echo = TRUE, warning = FALSE}
ITHIM <- createITHIM()
tilePlot(ITHIM, n = 25)
```

### 2017-02-28 R/appendix.Rmd

>>>>

### Appendix

Do it again, but with quintiles

```{r ITHIMObjsQuintiles, eval = FALSE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
DALYsTotal2 <- data.frame()
ITHIMList <- list()

ITHIM.default <- updateITHIM(ITHIM.default, "quantiles", seq(1, 9, by = 2)/10 )

ITHIM.national <- ITHIM.default
ITHIM.national <- updateITHIM(ITHIM.national, "muwt", muwtNational)
ITHIM.national <- updateITHIM(ITHIM.national, "muct", muctNational)
ITHIM.national <- updateITHIM(ITHIM.national, "Rwt", RwtNational)
ITHIM.national <- updateITHIM(ITHIM.national, "Rct", RctNational)

for (HHSTATE in stateVec){
    ITHIMList[[HHSTATE]] <- ITHIM.default
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "muwt", muwtList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "muct", muctList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "Rwt", RwtList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "Rct", RctList[[HHSTATE]])
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "GBD", ITHIM.national$parameters$GBD)
  }

for( muNonTravel in seq(0, upper, by = wd)){

  rm(DALYs)

  for (HHSTATE in stateVec){
    ITHIMList[[HHSTATE]] <- updateITHIM(ITHIMList[[HHSTATE]], "muNonTravel", muNonTravel)
  }

  ITHIM.national <- updateITHIM(ITHIM.national, "muNonTravel", muNonTravel)

  DALYs <- lapply(ITHIMList, sumDALY, ITHIM.baseline = ITHIM.national)
  DALYs <- data.frame(State = names(DALYs), muNonTravel = muNonTravel, DALY = unlist(DALYs))
  DALYsTotal2 <- rbind(DALYsTotal2, DALYs)
}

DALYsTotal2 <- within(DALYsTotal2, {
  State <- factor(State, levels = stateVecOrdered)
})

DALYsTotal <- rbind(data.frame(DALYsTotal,quints="Percentiles"), data.frame(DALYsTotal2,quints="Quintiles"))

p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY/1e3, colour = State))

p + stat_smooth( method = loess) + theme_bw() + scale_x_continuous(name="Mean Non-Travel METs (MET-hrs./week) (Referent Group)") + scale_y_continuous(name="Change in National DALYs (Thousands)") + coord_cartesian(xlim = c(0, upper)) + facet_grid( . ~ quints)

p + stat_smooth( method = loess) + theme_bw() + scale_x_continuous(name="Mean Non-Travel METs (MET-hrs./week) (Referent Group)") + scale_y_continuous(name="Change in National DALYs (Thousands)") + coord_cartesian(xlim = c(0, upper)) + geom_point() + facet_grid( . ~ quints)

### 2017-02-28 R/tutorial.Rmd

```{r libs, eval = TRUE, echo = TRUE, results = "show", warning = FALSE, error = FALSE, message = FALSE}
library("devtools")
install_github("syounkin/ITHIM", ref="master")
library("ITHIM")
date()
packageVersion("ITHIM")
```

@@

First we need to know the name of the parameters we want to update.
Currently the list of parameters resides in the help page for
"createParameterList".  We will find a better place for it.
Alternatively one can inspect the slots directly with slotNames.

```{r misc24, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
help(createParameterList)
slotNames(getParameterSet(ITHIM.baseline))
```

@@

```{r misc23, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
getMethodsITHIM()
meanVec <- getMeans(ITHIM.baseline)
meanWalkingTime <- meanVec$walk
meanCyclingTime <- meanVec$cycle
scenarioParameters <- list(muwt = 2*meanWalkingTime, muct = 2*meanCyclingTime)
scenarioParameters
```

@@

@@

```{r misc25, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
deltaBurden(ITHIM.baseline, ITHIM.scenario, dis = "total", bur = "daly.delta")
```

>>>>

```{r libs, eval = TRUE, echo = TRUE, results = "show", warning = FALSE, error = FALSE, message = FALSE}
library("devtools")
install_github("syounkin/ITHIM", ref="master")
library("ITHIM")
```

@@

First we need to know the name of the parameters we want to update.
Currently the list of parameters resides in the help page for the
ITHIM class.  Alternatively one can inspect the
slots directly with `slotNames`.

```{r misc24, message = FALSE, eval = FALSE, warning = FALSE, error = TRUE, echo = TRUE}
help("ITHIM")
```
or
```{r misc124, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
slotNames(getParameterSet(ITHIM.baseline))
```

@@

```{r misc23, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
getMethodsITHIM()
meanVec <- getMeans(ITHIM.baseline)
meanVec
meanWalkingTime <- meanVec$walk; meanCyclingTime <- meanVec$cycle
scenarioParameters <- list(muwt = 2*meanWalkingTime, muct = 2*meanCyclingTime)
scenarioParameters
```

Now we use the list of parameters and the baseline ITHIM object to
create the scenario ITHIM object.

@@

Let's inspect it to be sure.

```{r misc351, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
getMeans(ITHIM.scenario)
```

@@

```{r misc25, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
deltaBurden(ITHIM.baseline, ITHIM.scenario, dis = "total", bur = "deaths")
deltaBurden(ITHIM.baseline, ITHIM.scenario, dis = "BreastCancer", bur = "deaths")
deltaBurden(ITHIM.baseline, ITHIM.scenario, dis = "Depression", bur = "deaths")
deltaBurden(ITHIM.baseline, ITHIM.scenario, dis = "Depression", bur = "daly")
```

## Appendix

```{r misc350, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE, echo = TRUE}
ITHIM.baseline
ITHIM.scenario
```
### Session Info
```{r sessionInfo, eval = TRUE, echo = TRUE, results = "show", warning = FALSE, error = FALSE, message = FALSE}
sessionInfo()
```
